\section{Dataset analysis}

\subsection{Dataset presentation and modifications}

\subsubsection{Dataset presentation.}

We focus on two datasets. The first one is PEPSI, a compilation of synthetic flow observations generated from outputs of various hydraulic flow models. This dataset is composed of 55525 observations from 29 rivers worldwide, with 21 explanatory variables for each of them. The second dataset, HydroSwot is generated from observations -- from 153 rivers -- taken in-situ in North America. It contains 16638 observations with 41 explanatory variables. Table \ref{tab:varaibles} describes the explanatory variables contained in both datasets, and that we use for the statistic analysis.


\begin{table}[H]
    \centering
    \begin{tabular}{|c|c|c|c|}
    \hline
        Variable & Description & HydroSwot & PEPSI  \\ \hline \hline
        river &  river name & X & X \\ \hline
        site\_no & site number & X & \\ \hline
        day & simulation day & & X \\ \hline
        reach & reach index & &X \\ \hline
        reach\_length & length of the reach & & X \\ \hline 
        flowacc & flow accumulation, i.e. size of the upstream watershed & X & X \\ \hline
        height & free surface height & X & X \\ \hline 
        dH & water depth above unobserved flow & X & \\ \hline
        W &  free surface top width & X & X \\ \hline
        S & free surface slope  &  & X \\ \hline
        Sdem & terrain slope & X & \\ \hline
        K & Strickler value & & X \\ \hline
        Fr & Froude number & & X \\ \hline
        \alpha, \beta & Manning-Strickler coefficients & & X \\ \hline 
        A & cross-section flow area & & X \\ \hline 
        dA & cross-sectional flow area above A0 & X & X \\ \hline
        A0 & unobserved cross-sectional flow area & X & X\\ \hline
        Abar & mean cross-sectional flow area  data & X & X\\ \hline
        Amed & median cross-sectional flow area  data & X & \\ \hline
        U & flow velocity & X & X\\ \hline
        Q & discharge & X & X \\ \hline
        PA & mean annual precipitation & X & \\ \hline
        TA & mean annual temperature & X & \\ \hline
        sinuosity & sinuosity & & X \\ \hline 
        meandwave & meandering wavelenght & & X \\ \hline 
        Sand, salt, ... & floor composition & X &X \\ \hline 
        lon, lat & localisation & X & X \\ \hline 
        LC1, LC2, ... & vegetation information & X & \\ \hline 
        
    \end{tabular}
    \caption{Explanatory variables of HydroSwot and PEPSI datasets}
    \label{tab:varaibles}
\end{table}
\underline{Remark:} the values of the river discharge $Q$ have an uncertainty of 20\%. 


\subsubsection{Dataset modifications.\label{section212}}

First, we clean our datasets. We delete all observations with $NaN$ values, i.e. missing values. In the HydroSwot dataset, we can find different names for the same river because of text processing when creating the data. We update the names to have each river with a single name and make easier the analysis. We obtain 134 rivers.

The satellite does not detect small rivers with a width less than $80m$. Thus, we delete observations with a width under $80m$. We also remove observations with a river discharge under $100 m^3/s$ because we assume they are too precise observations, and so they do not have a real meaning.

We remove the calculations of base streamflow, and the different mean discharge quantile from the HydroSwot dataset. We also remove the flow velocity $U$ in the two datasets, because $U$ is linearly linked to $Q$ according to the following equation : $Q = AU$.\newline

Finally, we obtain a dataset with 29 rivers, 51269 observations, and 20 variables for PEPSI, and a dataset with 134 rivers, 11851 observations, and 21 variables for HydroSwot.
        
Due to previous modifications, we obtain only 1 observation for 8 sites in the HydroSwot dataset. We cannot use these data because the variables $dA$ and $dH$ are calculated by differences, so we must have at least 2 observations to give them meaning. Hence, we remove these 8 observations. To conclude, we lose 29\% of data in the HydroSwot dataset and 8\% in the PEPSI dataset.

\input{parties/Dataset analysis/methods_stat}

\input{parties/Dataset analysis/results_stat}
